### 2021-04-14 introduction.tex
Minor typographical updates.

The benefits of working with GV specifically, as opposed to other concurrent $\lambda$-calculi, is its relation to CP~\cite{wadler14}, and its strong formal properties. We thus pose our research question for GV:
\begin{quotation}
\textbf{RQ:} \emph{Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?}
\end{quotation}

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18} and PGV.
We make the following main contributions:
\begin{enumerate}
\item \textbf{Priority GV}. We present Priority GV (\secref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}). We addresses several problems in the original GV language, most notably:
  \begin{enumerate*}
  \item PGV does not require the pseudo-type $S^\sharp$; and
  \item its structural congruence is type preserving.
  \end{enumerate*}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item \textbf{Updated PCP}. We present an updated version of Priority CP~\cite{dardhagay18} (\secref{sec:pcp}). We remove commuting conversions and move away from reduction as cut elimination, and present a reduction relation based on structural congruence, as it is standard in process calculi.
\item \textbf{Translation from PCP to PGV}. We present a \emph{sound and complete encoding} of PCP in PGV (\secref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).
\end{enumerate}
\end{document}

>>>>

The benefits of working with GV specifically, as opposed to other concurrent $\lambda$-calculi, is its relation to CP~\cite{wadler14}, and its strong formal properties. We thus pose our research question for GV:
\begin{quotation}
  \textbf{RQ:}
  Can we design a more expressive GV which guarantees deadlock freedom for cyclic-structured processes?
\end{quotation}

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18} and PGV.
We make the following main contributions:
\begin{enumerate}[labelindent=0pt,labelwidth=1.333\parindent,align=left,labelsep*=0pt,leftmargin=!]
\item[(\secref{sec:pgv})] \textbf{Priority GV}. We present Priority GV (\secref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}). We addresses several problems in the original GV language, most notably:
  \begin{enumerate*}
  \item PGV does not require the pseudo-type $S^\sharp$; and
  \item its structural congruence is type preserving.
  \end{enumerate*}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item[(\secref{sec:pcp})] \textbf{Translation from PCP to PGV}.
  We present a \emph{sound and complete encoding} of Priority CP~\cite{dardhagay18} in PGV (\secref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).
  To obtain a tight correspondence, we update PCP, moving away from commuting conversions and reduction as cut elimination towards reduction based on structural congruence, as it is standard in process calculi.
\end{enumerate}
\end{document}
